# Presentation

### Kickoff
```{r}
load("D:/football/models.RData")
```


### ROC Curve 
```{r}
library(caTools)

# Predict on test: p
p1 <- predict(model_glm, data_cp, type = "prob")
# Make ROC curve
colAUC(p1, data_cp[["preferred_foot"]], plotROC = TRUE)
```

```{r}
# create list of model outcomes
model_resamples <- list(glm = model_glm, ctree = model_rpart, glmnet = model_glmnet, randomforest = model_rf) %>% 
  resamples()

# check out overview of model summaries
model_resamples %>% 
  summary()

# compare ROC means and spreads
model_resamples %>% 
  dotplot(metric = "ROC")

# Check for for outliers 
model_resamples %>% 
  densityplot(metric = "ROC")
```

# ROC Random Forest

```{r}
# Predict on test: p
p2 <- predict(model_rf, data_cp, type = "prob")
# Make ROC curve
colAUC(p2, data_cp[["preferred_foot"]], plotROC = TRUE)
```

### Explation

- Sensity is true positive rate
- Specifity is true negative rate
- Start and end are always (0,0) and (1,1)
- If line is above linear line then model is better than random guess
- AUC is max 1,0 * 1,0 = 1,0
- AUC for random guess is ~ 0,500
- Evaluates all possible thresholds for splitting probabilities
==> Choice, you can let the model predict more true positives and the cost off degrading certainty
==> Other choice, catch less true positives with greater certainty
